In this thesis we have studied the problem of finding the shortest path in a
plane with $k$ polygonal obstacle violations. First we showed a naive way for
computing this problem, by building a visibility graph and using Dijkstra to
find the shortest path with a maximum of $k$ allowed obstacle violation. This
could be done in $O(n^3 + k \cdot n^2 + \text{Dijkstra})$, where Dijkstra runs
in time $O((V + E) \log V)$. We implemented our naive algorithm and found our
implementation ran in the expected time. 

Next, we presented an optimal solution of solving the shortest path problem without obstacle violation, 
which is due to Hershberger and Suri\cite{HershbergerS99}, and presented an extension of this solution 
into one which could handle paths with obstacle violation, which is due to Hershberger, Kumar and Suri
\cite{HershbergerKS17}. 

We began our discussion of the Hershberger-Suri algorithm with the construction of a conforming 
subdivision which builds a grid on top of the plane which gives us some strong properties for subdividing 
it into a shortest path math. Here we considered both theoretical results and implementation details. 
Next, we presented the wavefront propagation which uses the conforming subdivision to construct 
the shortest path map, from which we can query the shortest path between a source point $s$ 
and an endpoint $t$ in time $O(\log n)$ \cite{DBLP:journals/siamcomp/Kirkpatrick83}. 

Next, we presented an extension of the Hershberger-Suri algorithm, with a needed modification
of the Hershberger-Suri algorithm and the overall algorithm which solves the shortest path with
$k$ polygonal obstacle violations in $k^2 \cdot n \log n)$ time. We also gave an overview of the
theory behind the solution to give a better understanding of the main ideas on which the algorithm
is constructed.

Finally we gave a reduction of finding a shortest path without obstacle violation to sorting numbers
and proved the optimally of the Hershberger-Suri algorithm.

\newpage 

\section{Future work}

Implementing the Hershberger Suri algorithm as described through chapters
\ref{chapter:conformingsubdivision} and \ref{chapter:wavefrontpropagation}
would seem quite natural as the next step in this process, though the sheer
complexity of it seems to make it a non trivial task. With such an
implementation, it would be interesting to measure its performance and compare
it to the naive $O(n^3)$ solution.

Also of interest would be an expansion of the bound of complexity for $SPM_k$
and general lower bound of a shortest $k$-path computation

